\documentclass[12pt]{article}
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[usenames]{color}

\leftmargin=0.25in
\oddsidemargin=0.25in
\textwidth=6.0in
\topmargin=-0.25in
\textheight=9.25in

\raggedright

%\pagenumbering{arabic}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }
% DEFINITIONS FOR RESUME

\newenvironment{changemargin}[2]{%
  \begin{list}{}{%
    \setlength{\topsep}{0pt}%
    \setlength{\leftmargin}{#1}%
    \setlength{\rightmargin}{#2}%
    \setlength{\listparindent}{\parindent}%
    \setlength{\itemindent}{\parindent}%
    \setlength{\parsep}{\parskip}%
  }%
  \item[]}{\end{list}
}

\newcommand{\lineover}{
	\begin{changemargin}{-0.05in}{-0.05in}
		\vspace*{-8pt}
		\hrulefill \\
		\vspace*{-2pt}
	\end{changemargin}
}

\newcommand{\header}[1]{
	\begin{changemargin}{-0.5in}{-0.5in}
		\scshape{#1}\\
  	\lineover
	\end{changemargin}
}

\newcommand{\contact}[4]{
	\begin{changemargin}{-0.5in}{-0.5in}
		\begin{center}
			{\Large \scshape {#1}}\\ \smallskip
			{#2}\\ \smallskip 
			{#3}\\ \smallskip
			{#4}\smallskip
		\end{center}
	\end{changemargin}
}

\newenvironment{body} {
	\vspace*{-16pt}
	\begin{changemargin}{-0.25in}{-0.5in}
  }	
	{\end{changemargin}
}	

\newcommand{\school}[4]{
	\textbf{#1} \hfill \emph{#2\\}
	#3\\ 
	#4\\
}

% END RESUME DEFINITIONS

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Name
\contact{Damir Garifullin}{gosugdr@gmail.com}{+7 (999) 208-5903}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Education
\header{Education}

\begin{body}
	\vspace{14pt}
	\textbf{B.S. Computer Science} \hfill \emph{Fall 2011 -- Spring 2015} \\
	\smallskip
	\emph{National Research University of Information Technologies, Mechanics and Optics} Saint-Petersburg, Russia\\
\end{body}

\smallskip


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Experience
\header{Career History}

\begin{body}
    \vspace{14pt}
	\textbf{Software Engineer}, \emph{IT Avia} \hfill \emph{Spring 2013 -- Fall 2013} and \emph{Summer 2014 -- Winter 2014}\\
	\vspace*{-4pt}
	\begin{itemize} \itemsep -0pt  % reduce space between items
		\item Developing software for airlines.
		\item Making access to remote desktop from browsers.
		\item Java, Javascript, C\#.
	\end{itemize}

	\smallskip

	\vspace{14pt}
	\textbf{Software Engineer}, \emph{Odnoklassniki.ru} \hfill \emph{Fall 2013 -- Summer 2014}\\
	\vspace*{-4pt}
	\begin{itemize} \itemsep -0pt  % reduce space between items
		\item Working on 2nd biggest social network in russian internet
		\item $\sim50$ million people everyday.
		\item Java, high perfomance.
		\item Securing accounts of users and administrators of communities
	\end{itemize}

    \smallskip

	\vspace{14pt}
	\textbf{PHP Developer}, \emph{Vkontakte} aka \emph{vk.com} \hfill \emph{Spring 2015 -- Spring 2015}\\
	\vspace*{-4pt}
	\begin{itemize} \itemsep -0pt  % reduce space between items
		\item Working on the biggest social network in russian internet
		\item $\sim75$ million people everyday.
		\item Internal tools and tools for ads.
		\item PHP, kPHP, high perfomance.
	\end{itemize}
    
    \smallskip
    
    \vspace{14pt}
	\textbf{Software Engineer}, \emph{IT Avia} \hfill \emph{Fall 2015 -- Present}
	\vspace*{-4pt}
	\begin{itemize} \itemsep -0pt  % reduce space between items
		\item Developing new functional for site and creating mobile applications for Android and iOS 
		\item Angular.js, CoffeeScript, JavaScript, Java, Swift.
	\end{itemize}

\end{body}

\smallskip
\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Skills
\header{Skills}

\begin{body}
	\vspace{14pt}
	\emph{\textbf{Programming:}}{}
	\begin{itemize}
		\item \textbf{Java} 5-6 years experience
        \subitem GWT, EJB, JUnit, MyBatis, Gradle, Maven, Spring, HighLoad 
		\item \textbf{C/C++} 9-10 years experience
        \subitem Mostly used in programming contests
		\item \textbf{Algorithms and Data Structures}
		\item \textbf{Android development} 
        \subitem Lots of opensource libraries
        \item \textbf{JavaScript, CoffeeScript, TypeScript, ES6}
        \subitem HTML/CSS, Grunt, Gulp, Bower, Ember, Angular, FRP
	\end{itemize}
	\emph{\textbf{Misc.:}}{} Microsoft SQL, SQLite, Cassandra,
    MySQL, PostgreSQL, Jasmin, Intellij Idea, Eclipse, 
	Unix(Arch linux), Vim, Docker, PHP, kPHP, LaTeX
\end{body}

\vspace{14pt}
\smallskip
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Personal qualities
\header{Personal qualities}

\begin{body}
	\vspace{14pt}
	Teamwork skills, flexibility, discipline, hardworking.
\end{body}

\smallskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Awards and Honors
\header{Awards and Honors}

\begin{body}
	\vspace{14pt}
	\textbf{All-Russian programming team contest} for high school students (final)\hfill \emph{\textbf{2010--2011}}\\
	\smallskip
	\textbf{All-Russian programming contest} for high school students (final)\hfill \emph{\textbf{2011}}\\
	\smallskip
	\textbf{ACM ICPC}, NEERC (semi-final) \hfill{} \emph{\textbf{2011}}\\
	\smallskip
	\vspace{14pt}
	I've been programming and participating in competitions like ACM ICPC since 2007 year. \\
	Took a part in a lot of programming training camps (Petrozavodsk) and contests (Hacker Cup, Google Code Jam, TopCoder, Codeforces etc.).\\
	\smallskip
	\textbf{Codeforces} \hfill{} \emph{in top \textbf{1000}}\\
	\smallskip
	\textbf{Facebook Hacker Cup} \hfill{} \emph{in top \textbf{250}}\\
	\smallskip
\end{body}

\end{document}
